---
title: "Writing fast R code"
author: "Violeta Garcia Saez & Yixuan Xu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

The package will contain three di↵erent functions for solving what is called the knapsack problem.
The knapsack problem is a discrete optimization problem where we have a knapsack that can take a
limited weight W and we want to fill this knapsack with a number of items i = 1, ..., n, each with a
weight w i and a value v i . The goal is to find the knapsack with the largest value of the elements added
to the knapsack. To solve this problem is NP which means that (most researchers belive) there are no
polynomial time algorithm to solve this problem.


## Report

this is Brute force search to solve the knapsack problem.

```{r}
library("fastcode")
library("parallel")
set.seed(42)
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500)
system.time(knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500))
```
  
this is Brute force search with multicore to solve the knapsack problem.

```{r}
knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500, parallel = TRUE)
system.time(knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500, parallel = TRUE))
```
  
This time we use Dynamic programming to solve the knapsack problem.

```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
system.time(knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500))
```
  
A last approach is to use the a heuristic or approximation for the problem.
  
```{r}
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
system.time(greedy_knapsack(x = knapsack_objects[1:800,], W = 3500))
```
  
now we will look at how long time does it takes to run the algorithm for n = 500 objects?  

```{r}
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```

And now How long time does it takes to run the algorithm for n = 10000 objects?

```{r}
set.seed(42)
n <- 2000
knapsack_objects1 <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
system.time(greedy_knapsack(x = knapsack_objects1[1:1000,], W = 3500))
```